Carbonate chemistry at Ny-Ålesund

### 2021-03-17 awipev-CO2.Rmd
k1k2 = "l" everywhere (except when s20 needed); ph_s normalized at 4°C

# Conversion of spec pH of in situ samples to in situ temp
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
pH_seafet <- pH_seafet %>% 
  dplyr::mutate(ph_s_sf_temp_insi = 
                  pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

@@

# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
# shown as white triangles on the plot
d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_insi,
      NA
    )
  )

@@

## Impact of choice of constants
### Lueker vs Sulpis using means of monthly means
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
monthly_means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
means <- monthly_means %>% 
  summarise(across(
    .cols = is.numeric, 
    .fns = mean, na.rm = TRUE, 
    .names = "{col}"
  ))

@@

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")
```
The means used are:
`r knitr::kable(means, format = "simple")`

### Lueker vs Sulpis using all values pCO2 and at_calc
One uses the pair pCO2-AT

>>>>

# Conversion of spec pH of in situ samples to in situ temp
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
pH_seafet <- pH_seafet %>% 
  dplyr::mutate(
    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
                         pHscale = "T", b="u74"),
   ph_s_sf_norm4 = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
                         pHscale = "T", b="u74")
  )

@@

d_all <- d_all %>%
  dplyr::mutate(ph_s_sf_norm4 = ifelse(!is.na(pH_seafet$ph_s_sf),
                                              pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
                         pHscale = "T", b="u74"), NA
  ))

# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available) shown as white triangles on the plot
# ALSO Conversion of spec pH of FerryBox samples at 4°C

d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_insi,
      NA
    ))

@@

## Impact of choice of constants
### Lueker vs Sulpis using means of monthly means
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above

# first, order columns
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all))) %>% 
  dplyr::select(datetime, date, year, monthd, montht, everything())

# calculate means
monthly_means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
means <- monthly_means %>% 
  summarise(across(
    .cols = is.numeric, 
    .fns = mean, na.rm = TRUE, 
    .names = "{col}"
  ))

@@

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
```
The means used are:
`r knitr::kable(means, format = "simple")`

The differences are:
`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")`

### Lueker vs Sulpis using all values pCO2 and at_calc
One uses the pair pCO2-AT_calc
